Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring

### 2020-06-01 manuscript.Rmd
Add descriptive caption

```{r cohesion-in-tweets, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = "Add more informative caption."}

# call figure 1 here

>>>>

```{r cohesion-in-tweets, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = "A visual representation of cohesion in tweets. Content word overlap indicates a shared relationship among tweets. The shared words--either identical or semantically similar--constitute a theme around which cohesion is occuring."}

# call the image
knitr::include_graphics("./figs/cohesion-in-tweets.png")
